\textbf{Computational Fuzzy Extractors}

### 2013-06-20 trunk/CompFuzzExt.tex
revisions to proof of 4.6

Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.    Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
\label{lem:i t poly time}
%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.  Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$.  It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
\end{lemma}

@@

In the information theoretic setting, Dodis et. al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.  A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
}
\bibliographystyle{alpha}
\bibliography{crypto}
\appendix
\section{Random Linear Codes Have High Distance}
%\subsection{Notions of Computational Entropy}
%\label{sec:notionsEntropy}
%In this sections we provide some further definitions of computational entropy.  HILL entropy is defined in \secref{sec:impossCompSecSketch}.  HILL entropy generalizes the notion of indistinguishability.  Yao entropy~\cite{DBLP:conf/focs/Yao82a, barak-computational} generalizes the notion of compressibility.  Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
%\begin{definition}
%\label{def:yao entropy}
%For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
%\[
%\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
%\]
%\end{definition}
%It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.  In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.  We also use a less common notion called unpredictability entropy.  This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
%Unpredictability entropy is a notion between HILL and Yao entropy:
%\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
%\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
%\]
%\end{lemma} 
%\subsection{Unique Witness Relations}

%We will need the ability to verify if we have a correct solution in~\consref{cons:informal construction}.  
%
%\begin{definition}
%Let $R$ be a relation.  We say that $R$ is $s_{ver}$-\emph{unique witness verifiable} if $\forall y$ there exists a unique $x$ such that $R(x, y)=1$ and $R(x, y) =1$ is computable in time $s_{ver}$.
%\end{definition}
%We can relax this definition slightly to allow a relation that is unique witness verifiable with all but negligible probability~(when $x, y$ grow with the security parameter).
%
%\begin{definition}
%\label{def:unique witness relation}
%Let $R:\mathcal{M}_1\times \mathcal{M}_2\rightarrow \zo$.  We say that $R$ is $(\epsilon, s_{ver})$-\emph{unique witness verifiable} if over $y\in \mathcal{M}_2$, drawn uniformly, the probability that $\exists x_1, x_2, x_1\neq x_2$ such that $R(x_1, y) =1 = R(x_2, y)$ is at most $\epsilon$ and $R$ is computable in time $s_{ver}$.
%\end{definition}
%
For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.  We will use the $q$-ary entropy function, denoted $H_q(x)$ and defined as $H_q(x) = x\log _q(q-1) - x\log_q x - (1-x)\log_q (1-x)$.  Note that $H_2(x) = -x\log x - (1-x)\log (1-x)$.  In the region $[0, \frac{1}{2}]$ for any value $q'\geq q$, $H_{q'}(x)\leq H_{q}(x)$.  The following theorem is standard in coding theory:

\begin{theorem}~\cite[Theorem 8]{venkatLecture}
\label{thm:random code good distance}
For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .  If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
\end{theorem}
Our setting is the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
\begin{corollary}
\label{cor:code high distance}
Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
Let $q$ be a prime and $\tau = O(\frac{m}{n}\log n )$.  For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $\tau$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
\end{corollary}
\begin{proof}
Let $c$ be some constant.  Let $\delta = \tau/m = \frac{c\log n}{n}$.  We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).  It suffices to show that for sufficiently large $n$, there exists $\epsilon>0$ where $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.  For sufficiently large $n$:
\begin{itemize}
\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.

% and note that there $\exists \epsilon$ where $0<\epsilon< 1-H_q(\frac{c\log n}{2n})< 1-H_q(\frac{c\log n}{m})$ and $1-H_q(c\log n/n) -\epsilon =1/2$ or equivalently $H_q(c\log n/n)+\epsilon = 1/2$.  Let $d$ be some constant such that $q< n^d$.  Consider the value of $H_q(\frac{c\log n}{n})$:
%\begin{align*}
%H_q(\frac{c\log n}{n})&\leq  H_{n^d}(\frac{c\log n}{n})\\
%&=\frac{c\log n}{n} \log_{n^d}(n^d-1) - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} (1-\frac{c\log n}{n})\\
%&\leq \frac{c\log n}{n}  - \frac{c\log n}{n} \log_{n^d} (\frac{c\log n}{n}) - (1-\frac{c\log n}{n})\log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n})-\log_{n^d} (\frac{n-c\log n}{n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
%&=\frac{c\log n}{n}  - \frac{c\log n}{n} \left(\log_{n^d} (\frac{c\log n}{n-c\log n}) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} (\frac{n}{c\log n}-1) \right)- \log_{n^d} \left(1-\frac{c\log n}{n}\right)\\
%&=\frac{c\log n}{n}  + \frac{c\log n}{n} \left(\log_{n^d} n \right)- \log_{n^d} \left(\frac{1}{n}\right)\\
%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} - \log_{n^d} \left(\frac{1}{n}\right)\\
%&\leq \frac{c\log n}{n}  + \frac{c\log n}{dn} + \frac{1}{d}
%\end{align*}
%Thus for large enough values of $n$, $H_{n^d}(\frac{c\log n}{n})\leq 1/2 + O(\frac{c\log n}{dn}) \leq 2/3$, thus $1 - H_q(\frac{c\log n}{n})> 1-H_{n^d}(\frac{c\log n}{n} )> 1/3$.  Taking $\epsilon  = 1/21/6$ the conditions of the corollary are satisfied.
\end{proof}

\ignore{
\section{Possibility of Constructing Computational Fuzzy Extractors}\label{ssec:constructing comp fuzzy extractors}
In the \secref{sec:imp HILL sketch}, we showed that defining a computational secure sketch using HILL entropy connects the parameters to the best constructible codes.  Thus, some entropy drop seems necessary when considering $H^\hill_{\epsilon, s}(X | SS(X))$.  However, in \propref{prop:prg comp fuzzy extractor}, we showed that a computational fuzzy extractor exists using a pseudorandom generator.  A natural question is whether this is necessary.  Do there exist clever constructions of computational fuzzy extractors that rely on the hardness of some cryptographic primitive that is easy within some distance $t$.  We begin by recalling the important parameters of a computational fuzzy extractor:
\begin{itemize}
\item The input entropy $m$.
\item The length of the output string $\ell$.  This output string is required to be $(\epsilon, s_{sec})$-pseudorandom.
\item The accepting distance $t$.
\end{itemize}
We consider the possibility of constructing a computational fuzzy extractor based on the remaining entropy of $W$ conditioned on the string $P$~(generated by $(R, P)\leftarrow \gen(W)$).  We first define a parameter $k_{prg}$.  Let $k_{prg}$ be the smallest integer such that there exists a pseudorandom generator from $k_{prg}$ to at least $k_{prg}+1$ bits.  More precisely, let $k_{prg}$ be the smallest integer such that there exists a deterministic function $prg:\{0,1\}^{k_{prg}}\rightarrow \{0,1 \}^{k_{prg}+1}$ such that $\forall D\in \mathcal{D}_s$: $\delta^D(prg(U_{k_{prg}}), U_{k_{prg}+1})<\epsilon$ for some negligible $\epsilon$ and super polynomial $s$.  We now classify the existence of computational fuzzy extractors based on this parameter.  Let $CODE$ be some error-correcting code with parameters, $(n, k, 2t+1)$.  We define $|CODE| = n-k$.

\begin{tabular}{c | c}
Remaining Entropy & Constructible?\\\hline
$CODE$ is computationally computable. & Yes, use \propref{prop:prg comp fuzzy extractor} \\
$H_\infty (W) - |CODE|\geq k_{prg}$\\\hline
$CODE$ exists, not necessarily efficiently computable. & Seems impossible to disprove, efficient\\
$H_\infty(W) - |CODE|\geq k_{prg}$ & construction of $CODE$ admits \propref{prop:prg comp fuzzy extractor}.\\\hline
Let $CODE$ be the best code. & Unknown, main area of interest\\
$H_\infty(W) - |CODE|< k_{prg}\leq H_\infty(W)$\\\hline 
$H_\infty(W)< k_{prg}$ & Seems to imply existence \\
&of improved $prg$ by using $\gen$.
\end{tabular}

We begin by focusing on the last case where $H_\infty(W) < k_{prg}$.  We first introduce two concepts, efficiently-generatable sources and sources that are $prg$ qualified.

\begin{definition}
A distribution $W$ over $\mathcal{M}$ is \emph{$(s_{gen}, \ell)$-efficiently-generatable} if there exists a deterministic circuit $G$ of size at most $s_{gen}$ such that $W \overset{d}= G(U_{\ell})$.
\end{definition}
\begin{definition}
A distribution $W$ over $\mathcal{M}$ is \emph{$(\epsilon, s, s_{f})$ - prg-qualified} if there exists a deterministic function $f:\mathcal{M}\rightarrow \{0,1\}^d$~(computable in space $s_{f}$) such that for all $D\in\mathcal{D}_s$, $\delta^D(f(W), U)<\epsilon$ and $d\geq k_{prg}$\footnote{We can extend this definition to allow $f$ to have public-randomness.  The definition is not meaningful if $f$ has private randomness as $f$ can simply generate a fresh seed of length $d$.}.
\end{definition}
We use the term prg-qualified as the composition of $f$ and a $prg$ gives pseudorandom bits:
\begin{proposition}
Let $W$ over $\mathcal{M}$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution with function $f$ to $d$ bits.  Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator~(computable by a circuit of size $s_{prg}$) where $k\leq d$.  Then $\forall D\in\mathcal{D}_{\min\{s_W-s_{prg}, s_{sec}\}}$
\[
\delta^D(prg(f(W)_{1,..., k}), U_{k+1})< \epsilon_W + \epsilon_{prg}.
\]
\end{proposition}
\begin{proof}
Let $W$ be a $(\epsilon_{W}, s_W, s_{f})$-prg-qualified distribution to $d$ bits.  Furthermore let $prg:\{0,1\}^k\rightarrow \{0,1\}^{k+1}$ be a $(\epsilon_{prg}, s_{sec})$- pseudorandom-generator where $k\leq d$.  We proceed by contradiction.  Suppose that $\exists D$ of size at most $s= \min\{s_W -s_{prg}, s_{sec}\}$ such that $\delta^D(prg(f(W)), U_{k+1})\geq \epsilon_W+\epsilon_{prg}$.  By the triangle inequality, one has:
\begin{align*}
\epsilon_W+\epsilon_{prg}&\leq \delta^D(prg(f(W)_{1,...,k}), U_{k+1})\\
&\leq \delta^D(prg(f(W)_{1,...,k}, prg(U_k)) + \delta^D(prg(U_k), U_{k+1})
\end{align*}
Thus, either $\delta^D(prg(f(W)_{1,...,k}, prg(U_k))\geq \epsilon_{W}$ or $\delta^D(prg(U_k), U_{k+1})\geq \epsilon_{prg}$.

In the first case, we construct a distinguisher $D'$ that contradicts the $(\epsilon_W, s_W, s_{f})$-qualification of $W$.  $D'$ upon receiving input $x\in \{0,1\}^d$ computes $D(prg(x))$ and outputs $D$'s answer.  $D'$ is of size at most $s + s_{prg} \leq s_W-s_{prg}+s_{prg} = s_W$ and has advantage at least $\epsilon_W$.  This is a contradiction.

In the second case, $D$ immediately contradicts the $(\epsilon_{prg}, s_{sec})$ security of $prg$.  Thus, we have a contradiction in both cases.  This completes the proof.
\end{proof}

We now return to the question of whether we can build a computational fuzzy extractor when $H_\infty(W)<k_{prg}$.
\begin{theorem}

\end{theorem}
\begin{proof}
\bnote{Do the proof!}
\end{proof}
}
%We now provide a candidate construction of fuzzy extractor based directly on a computational problem~(the LWE problem introduced by Regev~\cite{regevLWEsurvey}).
%\begin{definition}
%An $(\mathcal{M}, m, \tilde{m}, t, s_{dist}, \epsilon)$-\emph{computational secure sketch} is a pair of randomized algorithms, ``sketch'' (\sketch) and ``recover'' (\rec) with the following properties:
%\begin{enumerate}
%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns two strings, $(x,s)\in\{0,1\}^*$ where $x$ is drawn from a distribution $X$ and $\Hoo(X)\geq m$.
%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of a computational secure sketches guarantees that if $d(w,w')\leq t$, then $Rec(w', SS(w)_2) = SS(w)_1$.  
%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, observing $SS(W)_2$ does not significantly help the adversary.  That is, $H^\hill_{\epsilon, s_{dist}}(X | SS(W)_2)\geq \tilde{m}$.
%\end{enumerate}
%A secure sketch is \emph{efficient} if \sketch runs in expected polynomial time and \rec runs in expected polynomial time if $d(w', w) < t$.
%\end{definition}
%This definition has two significant changes from the definition of a secure sketch.  First, we do not require that the distribution $X$ is equal to the input distribution $W$.  This is because constructions will utilize computationally hard problems that may be difficult to invert.  However, we can consider the special case where $X=W$.  None of the power of a secure sketch is lost when $X\neq W$.

%\textbf{Note: }  The entropy of $X$ is somehow limited by the entropy of $X$ we cannot completely hide some very high entropy string, using a low entropy string.  This would have to be reflected in the parameters of \hill entropy but I am not yet sure how to formalize this.
%
% Furthermore, note there are two conditions on the distribution $X$, $\Hoo(X)\geq m$ and $H^\hill_{\epsilon, s}(X|SS(W)_2)\geq \tilde{m}$.  This means that if an adversary does not see the helper value $s$ it has true entropy and its computational entropy is decrease by seeing $s$.

%Second, we now require that the value $X$ only has conditional \hill entropy.  Considering the special case where $m=\tilde{m}$ is interesting but constructions that improve on the $\tilde{m}$ achieved in secure sketch are interesting.  Furthermore, it seems natural to consider the case where $|\rec|<s$ however, \rec has a significantly more difficult task, \rec must recover all of $x$ while the distinguisher in the conditional \hill entropy definition only needs to distinguish $x$ from a high average min-entropy distribution.
%
%Thus, we can define a stronger definition where all of these desiderata are achieved.  
%
%\begin{definition}
%A $(\mathcal{M}, m, \tilde{m}, t, s, \epsilon)$-computational secure sketch is strong if the following properties hold:
%\begin{enumerate}
%\item Seeing $s$ does not decrease the conditional $\hill$ entropy of $X$.  That is, $m=\tilde{m}$.
%\item There exists a circuit of \rec' where the size of \rec' is polynomial, $|\rec'|<s_{dist}$ and \rec' satisfies the correctness property.
%\end{enumerate}
%\end{definition}
\ignore{
\subsection{Learning With Errors (\class{LWE})}
\label{subsec:LWE in detail}
The LWE problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise". For positive integers $n$ and $q \ge 2$, a vector $\vect{s} \in \Fq$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{s}, \chi}$ be the distribution obtained by choosing a vector $\vect{a} \overset{\$}\leftarrow \Fq^n$ uniformly at random and a noise term $e \overset{\$}\leftarrow \chi$, and outputting $(\vect{a}, \langle \vect{a}, \vect{s}\rangle + e) \in (\Fq^m, \Fq)$. A formal definition follows.

\label{sec:LWEoverview}
\begin{problem}[\class{LWE}]\label{prob:LWE}
Let $n$ be the security parameter. For a integer $q = q(n)$ and the error distribution $\chi = \chi(n)$ over $\Fq$, the Learning With Error problem $\class{LWE}_{n, m, q,\chi}$ is defined as follows: given access to an oracle that outputs $m$ samples from $A_{\vect{s}, \chi}$ for a uniformly random $\vect{s}$, output $\vect{s}$ with high probability.
\end{problem}

We will use the fixed form of the LWE assumption where a matrix is prepared ahead of time.  The matrix form is as follows: $\class{LWE}$ find $\vect{x}$ given $(\vect{A},\vect{Ax+e})$, where $\vect{A}\leftarrow \Fq^{m \times n}$ is chosen uniformly and the error vector $\vect{e} \leftarrow \chi$.
Results of Regev~\cite{regev2005LWE} and Peikert~\cite{peikert2009latticereduction} connect the hardness of the LWE problem to solving worst-case lattice problems.  The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_\alpha$~(following the notation of~\cite{regev2005LWE}).  We denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$.  Here we present the theorem of~\cite{regev2005LWE}.

\begin{theorem}~\cite[Theorem 3.1]{regev2005LWE}
Let $n$ be a security parameter and $q = q(n) \in\Fq^+$, let $\alpha = \alpha(n)\in (0,1)$ be such that $\alpha q > 2\sqrt{n}$.  Let $\vA\in\Fq^{m\times n}, X\in \Fq^n$ be chosen uniformly at random and $E$ be chosen according to $\bar{\Psi}_\alpha$.  If there exists a PPT-algorithm $\mathcal{I}$ such that $\Pr_{\vA, X, E}[X\leftarrow  \mathcal{I}(\vA, \vA X+E) ]>\epsilon$ for some noticeable $\epsilon$, then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem~(GAPSVP) and the shortest independent vectors problem~(SIVP) to within $\Omega(n/\alpha)$ in the worst case.
\end{theorem}

We will consider a generalized assumption of \probref{prob:LWE}:
\begin{assumption}
\label{assume:general LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ and $q=q(n)\geq 2$ be integers and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, \vA\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{I}$ of size at most $s$
\[
\Pr_{\vA, X, E}[X\leftarrow \mathcal{I}(\vA, \vA X+E)]<\epsilon
\]
\end{assumption}
Furthermore, Regev shows a decision to search equivalence for $q=\poly(n)$, so we can consider an equivalent indistinguishability formulation:
\begin{assumption}
\label{assume:indist LWE}
Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, A\in\Fq^{m\times n}, B\in\Fq^m$ are chosen uniformly at random and $E$ is chosen according to $\chi$, then for all $\mathcal{D}$ of size at most $s$:
\[
\Pr[D(\vA, \vA X+E)=1]-\Pr[D(\vA, B)=1]<\epsilon
\]
\end{assumption}
We can restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy~(see Definition~\ref{def:unp entropy}).  
}

%\section{\lemref{lem:conversion to unpredictability}}
%\label{sec:proof of unpred conversion}
%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.  %We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).  Thus, we have the following claim:
%%\begin{claim}
%%\label{lem:unp of x and e}
%%Let $A, X, E$ be as above, then:
%%\begin{itemize}
%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
%%\end{itemize}
%%\end{claim}
%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
%%\begin{assumption}
%%\label{assume:entropy LWE}
%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.  
%%\end{assumption}
%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
%\label{lem:many hardcore bits}
%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
%\end{lemma}
%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.  Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.  Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.  By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.  To expand to $E$ we use the following claim:
%\begin{claim}
%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
%\[

>>>>

Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.    Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
\label{lem:i t poly time}
%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.  Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this probability is over the choice of random coins of \rep).  It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
\end{lemma}

@@

In the information theoretic setting, Dodis et. al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.  A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
}
\bibliographystyle{alpha}
\bibliography{crypto}
\appendix
\section{Properties of Random Linear Codes}
For efficient decoding of \consref{cons:informal construction}, we need the $\LWE$ instance to have high distance with overwhelming probability.  We will use the $q$-ary entropy function, denoted $H_q(x)$ and defined as $H_q(x) = x\log _q(q-1) - x\log_q x - (1-x)\log_q (1-x)$.  Note that $H_2(x) = -x\log x - (1-x)\log (1-x)$.  In the region $[0, \frac{1}{2}]$ for any value $q'\geq q$, $H_{q'}(x)\leq H_{q}(x)$.  The following theorem is standard in coding theory:

\begin{theorem}~\cite[Theorem 8]{venkatLecture}
\label{thm:random code good distance}
For prime $q, \delta\in [0, 1-1/q), 0<\epsilon< 1-H_q(\delta)$ and sufficiently large $m$, the following holds for $n = \lceil (1-H_q(\delta) - \epsilon)m\rceil$ .  If $\vA \in \Fq^{m\times n}$ is drawn uniformly at random, then the linear code with $\vA$ as a generator matrix has rate at least $(1-H_q(\delta) -\epsilon)$ and relative distance at least $\delta$ with probability at least $1-e^{-\Omega(m)}$.
\end{theorem}
Our setting is the case where $m = poly(n)\geq 2n$ and $\delta = O (\log n /n)$.  This setting of parameters satisfies \thref{thm:random code good distance}:
\begin{corollary}
\label{cor:code high distance}
Let $n$ be a parameter and let $m = \poly(n)\geq 2n$.  
Let $q$ be a prime and $\tau = O(\frac{m}{n}\log n )$.  For large enough values of $n$, when $\vA\in \Fq^{m\times n}$ is drawn uniformly, the code generated by $\vA$ has distance at least $\tau$ with probability at least $1-e^{-\Omega(m)}\geq 1-e^{-\Omega(n)}$.
\end{corollary}
\begin{proof}
Let $c$ be some constant.  Let $\delta = \tau/m = \frac{c\log n}{n}$.  We show the corollary for the case when $m = 2n$~(increasing the size of $m$ only increases the relative distance).  It suffices to show that for sufficiently large $n$, there exists $\epsilon>0$ where $1- H_q(\frac{c\log n}{n}) - \epsilon = 1/2$ or equivalently that $H_q(\frac{c\log n}{m})< 1/2$ as then setting $\epsilon = 1/2-H_q(\frac{c\log n}{n})$ satisfies  \thref{thm:random code good distance}.  For sufficiently large $n$:
\begin{itemize}
\item $\frac{c\log n}{n}< 1/2$, so we can work with the binary entropy function $H_2$.  
\item $\frac{c\log n}{n}< .1 < 1/2$ and thus $H_q(\frac{c\log n}{n})< H_q(.1)$. 
\end{itemize}  Putting these statements together, for large enough $n$, $H_q(\frac{c\log n}{n})< H_q(.1) < H_2(.1)< 1/2$ as desired.  This completes the proof.
\end{proof}

We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \alpha q^{\beta}$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }= \alpha q^{-\beta}.
\end{align*}
\end{proof}
